% This is a copy version from https://github.com/thanhhungqb/thesis-template
% Please do not modified this project, when you want to start writing, make a clone of it for your own (Please read README.md)

\documentclass[12pt,a4paper,oneside]{book} % twoside for draf

%\usepackage{babel}
\usepackage[utf8]{vietnam}
\usepackage[utf8]{inputenc}
\usepackage[vietnamese,english]{babel}

\usepackage{tipa}
\usepackage{amssymb}
\usepackage{graphicx, wrapfig}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{mathptmx}	% same Time New Roma
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{sty/ipa}
%\renewcommand{\rmdefault}{phv} % Arial
%\renewcommand{\sfdefault}{phv} % Arial
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{algorithm2e}
\usepackage{hyperref}
\usepackage{float}
\usepackage{longtable}

\usepackage{sty/bkthesis}

% \usepackage[
% backend=biber,
% style=alphabetic,
% ]{biblatex}
% \addbibresource{refs.bib}

% To numbering figure continuously
\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.2}

\graphicspath{ {image/} }
\setcounter{secnumdepth}{2}
\crname{GRADUATION THESIS}
% \ctname{NHẬN DIỆN VẬT THỂ TRONG ẢNH\\NHẬN DIỆN HƯỚNG NHÌN TRONG ẢNH}
\ctname{USING MACHINE LEARNING METHODS\\IN TRANSLATING SIGN LANGUAGE\\INTO VIETNAMESE}
\cstuname{STUDENT 1: Võ Tuấn Khanh (1810220)}
\cstunameOne{STUDENT 2: Nguyễn Trí Nhân (1810390)}
\csSupervise{Assoc. Prof. Quản Thành Thơ}
\csReviewer{Mr. Trần Hồng Tài, MSc}

\cttime{05/2022}

\thesislayout

\begin{document}
%-	Bìa cứng - màu xanh dương, chữ mạ vàng (xem mẫu đính kèm)
%-	Trang tên (tờ lót): chất liệu giấy, nội dung giống như bìa LV
%-	Ở gáy LV: in nhan đề LV (có thể in tóm tắt nếu nhan đề quá dài), size 15 – 17
%-	Phiếu Nhiệm vụ LV, chấm điểm Hướng dẫn & Phản biện (đã ký): nhận từ GVHD & GVPB sau khi bảo vệ (theo lịch hẹn).
%-	Lời cam đoan
%-	Lời cảm ơn/ Lời ngỏ
%-	Tóm tắt LV
%-	Mục lục
%-	Danh mục, bảng biểu, hình ảnh, ... (nếu có)
%-	Nội dung LV
%-	Danh mục TL tham khảo
%-	Phụ lục (nếu có)

\coverpage

\frontmatter


\begin{declaration}
	% ví dụ:

	% Nhận diện hướng nhìn trong ảnh (Nhận diện vật thể trong ảnh) không phải là một đề tài mới nhưng vẫn là một thách thức bởi: trong các ứng dụng: việc nhận diện hướng nhìn của con người qua hình ảnh đòi hỏi kết quả chính xác cao, ở Việt Nam, hiện tại không  thực sự có nhiều nghiên cứu chuyên sâu về đề tài. Trong quá trình nghiên cứu đề tài có rất nhiều kiến thức không nằm trong chương trình giảng dạy ở bậc Đại học tuy vậy chúng tôi xin cam đoan đây là công trình nghiên cứu của riêng tôi dưới sự hướng dẫn của tiến sĩ Nguyễn Đức Dũng. Nội dung nghiên cứu và các kết quả đều là trung thực và chưa từng được công bố trước đây. Các số liệu được sử dụng cho quá trình phân tích, nhận xét được chính tôi thu thập từ nhiều nguồn khác nhau và sẽ được ghi rõ trong phần tài liệu tham khảo.

  % Ngoài ra, tôi cũng có sử dụng một số nhận xét, đánh giá và số liệu của các tác giả khác, cơ quan tổ chức khác. Tất cả đều có trích dẫn và chú thích nguồn gốc.

  % Nếu phát hiện có bất kì sự gian lận nào, tôi xin hoàn toàn chịu trách nhiệm về nội dung luận văn của mình. Trường đại học Bách Khoa thành phố Hồ Chí Minh không liên quan đến những vi phạm tác quyền, bản quyền do tôi gây ra trong quá trình thực hiện.

We claim that this research is our work, conducted under the supervision and guidance of Associate Professor Quản Thành Thơ. The result of our research is authentic and has never been published in any way before. All the materials I utilized in this research were gathered from various sources and are referenced correctly in the references section. 

Furthermore, within this research, I also used the results of several other authors and organizations. All of them have been correctly cited. In any case of plagiarism, I stand by my actions and will be responsible for it. Therefore, Ho Chi Minh City University of Technology is not responsible for any copyright infringements conducted within our research.

\end{declaration}

\begin{acknowledgments}

To complete this thesis outline, I would like to express my deep gratitude to Associate Professor Quản Thành Thơ for his guidance throughout the research process.

We want to express our sincere thanks to the Faculty of Computer Science and Engineering teachers, Ho Chi Minh City University of Technology, for their dedication to imparting knowledge during our years of study at the school. The knowledge accumulated during the study process is the foundation for the research process and the luggage to enter life confidently.

Finally, I wish you good health and success in your noble career.
	
\end{acknowledgments}
	
\begin{abstract}

Presently, more than two million people with deaf and hard of hearing in Vietnam cannot talk freely with those who do not have those symptoms. There are a few ways for the deaf and hard of hearing to communicate with others, but they are ineffective and inefficient. The most used method is through notes or body language to express their thoughts to others. However, not many people know about sign language, making it hard to understand.

To help those people communicate more efficiently, we have built a system using Artificial Intelligence to translate sign language into Vietnamese. The design, in short, contains two physical modules, which are a camera and a smartphone having installed our application. Beneath the application is an Artificial Intelligence-based pipeline with six more submodules that translate sign language into text and read the word out loud through the phone’s built-in speaker.

Besides, the sign language data is collected from various resources through the site \url{https://tudienngonngukyhieu.com/} and \url{https://qipedc.moet.gov.vn/}. Based on the videos that instruct vocabularies, we gathered and categorized them for the primary dataset of this system.

Overall, our system currently can translate some words. However, the more time it takes to learn the new terms, the more accurate the system is. The system can translate many more words with a much more extensive sign language library. We suppose our approach not only helps people with disabilities communicate and enrich their lives, but it also increases the volume of the workforce and reduces the economic burden on the national budget since then.

\end{abstract}	


\tableofcontents
% \listofsymbols
\listoffigures
\listoftables
%\listofalgorithms


\mainmatter

\fancyhead{}  % Clears all page headers and footers
%\rhead{\thepage}  % Sets the right side header to show the page number
%\lhead{}  % Clears the left side page header
%\fancyfoot[positions]{footer}
\renewcommand{\footrulewidth}{0.4pt}

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers
%

\input{chapter/chapter1-introduction.tex}
\input{chapter/chapter2-relatedWork.tex}
\input{chapter/chapter3-theoreticalBackground.tex}
\input{chapter/chapter4-designAndSolution.tex}
% \input{chapter/chapter5-upcomingPlan.tex}
% \input{chapter/chapter6-proposedThesisChapters.tex}
% \input{chapter/chapter5-implementation.tex}
\input{chapter/chapter6-resultAndEvaluation.tex}

\input{chapter/chapter7-summary.tex}

\newpage
%-	Danh mục TL tham khảo
%-	Phụ lục (nếu có)
\bibliographystyle{plain}
\bibliography{refs}

\end{document}