\chapter{Summary}

The thesis has applied image processing and artificial intelligence to research and develop a system capable of translating sign language into Vietnamese using only a camera module and a smartphone.

Aside from the system's two main features, the team is working on another feature that will help people learn sign language using the spaced repetition technique. There have been numerous studies and research papers published on this technique, and it is widely regarded as the most effective method for learning anything.

Because of the complexity of sign language and the diversity of ways people use it around the world, developing a sign language translating system has been a massive challenge for many scientists and engineers. Furthermore, when we were researching and developing the system, we discovered a few similar systems that only translated the sign language alphabet.

Additionally, in terms of human values, this system has the potential to address Vietnam's shortage of sign-language translators. It does, indeed, imply that people with disabilities will be able to live, work, and communicate in the same way as those who do not. They will receive a better education because the teacher will be able to understand and connect their thoughts more effectively. They can have better health because the health force will be able to learn more about how they are and what they are feeling, allowing us to better treat their problems. Their lives will be made easier as people around them can see and talk to them more clearly.

The deaf and deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deafeningly deaf As a result, we believe that the deaf and mute deserve the opportunity to speak up, be heard, be seen, and be recognized. We can get to know each other and communicate fluently using this app, regardless of our level of sign language knowledge. Our bonds will eventually become more vital and profound, leading to a better world for the entire human race.

These human values emphasize the significance of this project in our world. Separated from the aforementioned, the aforementioned, and the aforementioned, and the aforementioned, and the aforementioned, and the aforementioned, and the We will have more resources to devote to completing our algorithm in the future, which will result in higher accuracy of the translation process and thorough completion of the thesis.
