\chapter{Proposed Thesis Chapters}

\textbf{Chapter 1. Overview.} In the chapter, we will present the reason for choosing this topic, \textbf{Using machine learning methods to translate sign language into Vietnamese}; Introducing the related works, raising the challenges when doing the research and building the system; then presenting the aim, scope, and structure of the thesis.

\textbf{Chapter 2. Related works.} This chapter contains the associated works that we have referenced when doing the thesis and how they help us build the system.

\textbf{Chapter 3. Theoretical background.} This chapter show all the foundation knowledge that are applied in the thesis, and their assistance in completing the thesis. 

\textbf{Chapter 4. Proposed system.} We will analyze the main problem and break it down into pieces to develop the solution for the sub-problems; We also present the design of the system structure, the application, and how they are connected.

\textbf{Chapter 5. Database.} This chapter will show the data used in the thesis from its fundamental definition, to the way we collect and process them in order to train the learning model.

\textbf{Chapter 6. Implementation.} We will present the steps to build the system, including setting up the environment, programming the server, application, the physical module, and connecting them so that they can work precisely.

\textbf{Chapter 7. Result and evaluation.} This chapter contains how to use the system, convey the outcome when using it; And evaluate the accuracy rate to ensure it is ready to be used.

\textbf{Chapter 8. Summary.} In the last chapter, we will summarize the whole system, its implementation, result and evaluate them to emphasize the good and bad of the system; Moreover, we will suggest the plan to develop this system in the future.
